Graphics

### 2020-06-03 individual-cohorts/graphics_t_statistics.Rmd
improve plot and text size

```{r functions}
plot_t <- function(df, conditions){
  p = list()
  for(i in seq_along(conditions[,1])){
  positions = conditions[i,]
  x = df[positions[1]]
  y = df[positions[2]]
  computed_cor = cor(x, y, method = "spearman")
  x_var <- names(x)
  y_var <- names(y)
  p[[i]] = ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]])) +
  geom_hex() +
  geom_abline() +
  theme_bw() +
  labs(
    caption = paste0("spearman correlation between the statistics is ", round(computed_cor, digits = 3))
  ) +
    theme(aspect.ratio=1)
  }
multiplot(plotlist = p, cols = 2)
}
```

@@

#Remove transcript Ids
df_one <- df_one %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df_one <- inner_join(df_one, dplyr::select(gandal, gene_id,  `Gandal, BD t-statistic`,`Gandal, ASD t-statistic`), by = c("gene_id")) %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

@@

```{r heatmapa, fig.width = 5, fig.height = 5 }
colnames(df_one) <- gsub(" t-statistic", "", colnames(df_one))

@@

Heatmap(as.matrix(cor$r), 
        name = "spearman cor", 
        rect_gp = gpar(col = "white", lwd = 2),
        column_names_rot = 45,
        col = colors,
        row_names_gp = gpar(fontsize = 10),
        column_names_gp = gpar(fontsize = 10),
        cell_fun = function(j, i, x, y, width, height, fill) {
        grid.text(sprintf("%.1f", as.matrix(cor$r)[i, j]), x, y, gp = gpar(fontsize = 8))
          }
        )
```

@@

#Remove transcript Ids
df_two <- df_two %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df_two <- inner_join(df_two, CMC1, by = c("gene_id")) 
df_two <- inner_join(df_two, CMC_HBCC, by = c("gene_id"))
df_two <- inner_join(df_two, dplyr::select(gandal, gene_id, `Gandal, SCZ t-statistic`), by = c("gene_id")) %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

@@

```{r heatmapb, fig.width = 8, fig.height = 8 }
colnames(df_two) <- gsub(" t-statistic", "", colnames(df_two))

@@

#Remove transcript Ids
df_three <- df_three %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df_three <- inner_join(df_three, dplyr::select(gandal, gene_id,  `Gandal, BD t-statistic`,`Gandal, ASD t-statistic`), by = c("gene_id")) %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

>>>>

```{r functions}
plot_t <- function(df, conditions){
  p = list()
  for(i in seq_along(conditions[,1])){
  positions = conditions[i,]
  x = df[positions[1]]
  y = df[positions[2]]
  computed_cor = cor(x, y, method = "spearman")
  x_var <- names(x)
  y_var <- names(y)
  p[[i]] = ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]])) +
  geom_hex() +
  geom_abline() +
  theme_bw() +
  labs(
    caption = paste0("spearman correlation between the statistics is ", round(computed_cor, digits = 3))
  ) +
    theme(aspect.ratio=1, 
          axis.text=element_text(size=12),
          plot.caption = element_text(face = "bold", size = "12"))
  }
multiplot(plotlist = p, cols = 2)
}
```

@@

#Remove transcript Ids
df_one <- df_one %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df_one <- inner_join(df_one, dplyr::select(gandal, gene_id,  `Gandal, SCZ t-statistic`,`Gandal, BD t-statistic`,`Gandal, ASD t-statistic`), by = c("gene_id")) %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

@@

```{r heatmapa, fig.width = 8, fig.height = 8 }
colnames(df_one) <- gsub(" t-statistic", "", colnames(df_one))

@@

Heatmap(as.matrix(cor$r), 
        name = "spearman cor", 
        rect_gp = gpar(col = "white", lwd = 2),
        column_names_rot = 45,
        col = colors,
        row_names_gp = gpar(fontsize = 12),
        column_names_gp = gpar(fontsize = 12),
        cell_fun = function(j, i, x, y, width, height, fill) {
        grid.text(sprintf("%.1f", as.matrix(cor$r)[i, j]), x, y, gp = gpar(fontsize = 12))
          }
        )
```

@@

#Remove transcript Ids
df_two <- df_two %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df_two <- inner_join(df_two, CMC1, by = c("gene_id")) 
df_two <- inner_join(df_two, CMC_HBCC, by = c("gene_id"))
df_two <- inner_join(df_two, dplyr::select(gandal, gene_id, `Gandal, SCZ t-statistic`, 
                                           `Gandal, ASD t-statistic`, `Gandal, BD t-statistic`), by = c("gene_id")) %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

@@

```{r heatmapb, fig.width = 5, fig.height = 5 }
colnames(df_two) <- gsub(" t-statistic", "", colnames(df_two))

@@

#Remove transcript Ids
df_three <- df_three %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df_three <- inner_join(df_three, dplyr::select(gandal, gene_id,  `Gandal, BD t-statistic`,
                                               `Gandal, ASD t-statistic`, `Gandal, SCZ t-statistic`), by = c("gene_id")) %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")
